Intercoder ICBEdataset_figure_semantic_embeddings

### 2022-02-07 README.Rmd
paper run1

  - CaseStudy196
      + creates Cuban Missile Crisis comparison table `/tables/CaseStudy196_ft.Rds`. 
  - CaseStudy426
  - ICBEdataset_figure_metro_maps
  - ICBEdataset_figure_semantic_embeddings
  - ICBEdataset_paper_appendixICBCrises
  - ICBEdataset_paper_appendixVerbMeanings
  - ICBEdataset_paper_figure_prep
  - ICBEdataset_paper_litreviewtable
  - ICBEdataset_paper_PlotInterCoderAgreement

@@

### External datasets
  - [The ICB project](https://sites.duke.edu/icbdata/) 
    + System-level (./data/icb1v14.Rds) and Actor-level (./data/icb2v14.Rds) datasets
    + Dyadic-Level Crisis Data ([source](https://sites.duke.edu/icbdata/data-collections/))
  - [Militarized Interstate Disputes (MID)](https://correlatesofwar.org/data-sets/MIDs) version 5.01 at the incident level (MIDI 5.01) and incident-participant level (MIDIP 5.01) converted to Rds. 
  - [UCDP Georeferenced Event Dataset (GED) Global version 21.1](https://ucdp.uu.se/downloads/index.html#ged_global)
  - cameo.eventcode.txt adapted from [CAMEO Conflict and Mediation Event Observations Codebook](https://parusanalytics.com/eventdata/cameo.dir/CAMEO.09b6.pdf)
  - [Phoenix Event data](https://databank.illinois.edu/datasets/IDB-2796521)
  - [Terrier event data](https://osf.io/4m2u7/files/) 
    + too large to include in the github repository
    + to replicate, download the folder 'largegeolocatedata' to ICBEdata/replication_paper/data/ignore and decompress
  - [ICEWS data sample](https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/28075&version=30.0) from 1995 (./inst/extdata/icews.actors.20181119.RData)
    + too large to include in the github repository
    + to replicate, download the .tsv and .tab files to ICBEdata/replication_paper/data/ignore/icews_dataverse/ and decompress

>>>>

  - CaseStudy196
      + creates Cuban Missile Crisis comparison table `/tables/CaseStudy196_ft.Rds`. 
  - CaseStudy426
      + creates DRC Civil War comparison table `/tables/CaseStudy426_ft.Rds`. 
  - ICBEdataset_figure_metro_maps
      + creates the metroplot figures in `/figures/metro_plots/.`.
  - ICBEdataset_figure_semantic_embeddings
  - ICBEdataset_paper_appendixICBCrises
  - ICBEdataset_paper_appendixVerbMeanings
  - ICBEdataset_paper_figure_prep
  - ICBEdataset_paper_litreviewtable
  - ICBEdataset_paper_PlotInterCoderAgreement

@@

### External datasets
  - [The ICB project](https://sites.duke.edu/icbdata/) 
    + System-level (./data/icb1v14.Rds) and Actor-level (./data/icb2v14.Rds) datasets
    + Dyadic-Level Crisis Data ([source](https://sites.duke.edu/icbdata/data-collections/))
  - [Militarized Interstate Disputes (MID)](https://correlatesofwar.org/data-sets/MIDs) version 5.01 at the incident level (MIDI 5.01) and incident-participant level (MIDIP 5.01) converted to Rds. 
  - [UCDP Georeferenced Event Dataset (GED) Global version 21.1](https://ucdp.uu.se/downloads/index.html#ged_global)
  - cameo.eventcode.txt adapted from [CAMEO Conflict and Mediation Event Observations Codebook](https://parusanalytics.com/eventdata/cameo.dir/CAMEO.09b6.pdf)
  - [Phoenix Event data](https://databank.illinois.edu/datasets/IDB-2796521)
  - [Terrier event data](https://osf.io/4m2u7/files/) 
    + too large to include in the github repository
    + to replicate, download the folder 'largegeolocatedata' to ICBEdata/replication_paper/data/ignore and decompress
  - [ICEWS data](https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/28075&version=30.0)
    + too large to include in the github repository
    + to replicate, download folder 'dataverse_files' to ICBEdata/replication_paper/data/ignore/ and decompress

### 2022-02-07 replication_paper/rmd/ICBEdataset_figure_metro_maps.Rmd
paper run1

@@

Go ahead an out the sentence tables too here why not

@@

ged211 <- read_csv(paste0(here::here(), "/replication_paper/data/ignore/ged/ged211.csv"))

@@

@@

#Rex start here tomorrow, figure out how to do this join correctly
actor_translator_icews <- actor_translator %>%  dplyr::select(ICEWS_Actor.Name, ICEWS_Country, QCode, QCode_name)
#%>% mutate(icews=ifelse(ICEWS_Country=="International Government Organizations", ICEWS_Actor.Name, ICEWS_Country))

@@

@@

#Maybe it's just ISO3 country codes?
terrier_clean <- terrier %>% 
    dplyr::select(
      cameo_code=x3,
      src_country=x8,
      src_agent=x9,
      src_other_agent=x10,

@@

      year=x17,
      month=x18,
      day=x19#,
      #random_text=x28
    ) %>% 
    filter(!is.na(src_country) & !is.na(target_country)) %>%
    distinct() %>% 
     mutate(cameo_code=cameo_code %>% as.numeric()) %>% 
     left_join(CAMEO_eventcodes %>% mutate(cameo_code=cameo_code %>% as.numeric()) %>%
                 dplyr::select(cameo_code=cameo_code, cameo_label= cameo_label)  ) %>%
    mutate( cameo_label= cameo_label %>% str_replace(', not specified below','')) %>%
    distinct() %>%

@@

   left_join(df %>% dplyr::select(src_other_agent=agent   , src_other_agent_label=agent_label) %>% distinct() %>% na.omit() ) %>%
   left_join(df %>% dplyr::select(target_other_agent=agent, target_other_agent_label=agent_label) %>% distinct() %>% na.omit() ) %>%

   left_join(df %>% dplyr::select(src_agent=agent, src_agent_label=agent_label) %>% distinct() %>% na.omit() ) %>%
   left_join(df %>% dplyr::select(target_agent=agent, target_agent_label=agent_label) %>% distinct() %>% na.omit() )  %>% 
   distinct() %>%
   filter(
     !src_other_agent_label %in% role_rejects &
     !target_other_agent_label %in% role_rejects &
     !src_agent_label %in% role_rejects &
     !target_agent_label %in% role_rejects 
     ) %>% 
  left_join(actor_translator %>% dplyr::select(src_country=terrier,actor_1_qcode=QCode,actor_1=QCode_name) ) %>%
  left_join(actor_translator %>% dplyr::select(target_country=terrier,actor_2_qcode=QCode,actor_2=QCode_name) ) %>%
  filter(!is.na(actor_1_qcode) & !is.na(actor_2_qcode) ) %>%
  mutate(source_root_target=paste0(src_country, "_", target_country) ) %>%
  mutate(
  event_date= lubridate::as_date(paste0( year, "-", month,"-",day ))
  )
dim(terrier_clean) #2,049,759

>>>>

  actors=codings_wide_agreed_subset_nodes$actor %>% unique() %>% as.factor()
  actor_colors = c(brewer.pal(n=11, "Dark2"), brewer.pal(n=11, "Set1"))[1:length(actors)] #pick a bewer pallet with lots of values and then assign it to specific values
  names(actor_colors) = levels(actors)

@@

out the sentence tables

@@

load(paste0(here::here(), "/replication_paper/data/in/GEDEvent_v21_1.RData"))
ged211 <- GEDEvent_v21_1

#ged211 <- read_csv(paste0(here::here(), "/replication_paper/data/ignore/ged211.csv"))

@@

if(!file.exists(paste0(here::here(), "/replication_paper/data/ignore/icews_dataverse/dataverse_files/"))){
  stop("Missing 'UCDP Georeferenced Event Dataset (GED)'. See README.")
}

@@

actor_translator_icews <- actor_translator %>%  dplyr::select(ICEWS_Actor.Name, ICEWS_Country, QCode, QCode_name)
#%>% mutate(icews=ifelse(ICEWS_Country=="International Government Organizations", ICEWS_Actor.Name, ICEWS_Country))

@@

if(!file.exists(paste0(here::here(), "/replication_paper/data/ignore/terrier/largegeolocateddata//"))){
  stop("Missing Terrier event data. See README.")
}

@@

```{r}
#Maybe it's just ISO3 country codes?
terrier_clean_temp <- terrier %>% 
    dplyr::select(
      cameo_code=x3,
      src_country=x8,
      src_agent=x9,
      src_other_agent=x10,

@@

      year=x17,
      month=x18,
      day=x19#,
      #random_text=x28
    ) %>% 
    filter(!is.na(src_country) & !is.na(target_country)) %>%
    distinct() %>% 
     mutate(cameo_code=cameo_code %>% as.numeric()) %>% 
     left_join(CAMEO_eventcodes %>% mutate(cameo_code=cameo_code %>% as.numeric()) %>%
                 dplyr::select(cameo_code=cameo_code, cameo_label= cameo_label)  ) %>%
    mutate( cameo_label= cameo_label %>% str_replace(', not specified below','')) %>%
    distinct()

#done

```{r}
terrier_clean_temp <- terrier_clean_temp %>%

@@

   left_join(df %>% dplyr::select(src_other_agent=agent   , src_other_agent_label=agent_label) %>% distinct() %>% na.omit() ) %>%
   left_join(df %>% dplyr::select(target_other_agent=agent, target_other_agent_label=agent_label) %>% distinct() %>% na.omit() )

```{r}
terrier_clean <- terrier_clean_temp %>%
     left_join(df %>% dplyr::select(src_agent=agent, src_agent_label=agent_label) %>% distinct() %>% na.omit() ) %>%
   left_join(df %>% dplyr::select(target_agent=agent, target_agent_label=agent_label) %>% distinct() %>% na.omit() )  %>% 
   distinct() %>%
   filter(
     !src_other_agent_label %in% role_rejects &
     !target_other_agent_label %in% role_rejects &
     !src_agent_label %in% role_rejects &
     !target_agent_label %in% role_rejects 
     ) %>% 
  left_join(actor_translator %>% dplyr::select(src_country=terrier,actor_1_qcode=QCode,actor_1=QCode_name) ) %>%
  left_join(actor_translator %>% dplyr::select(target_country=terrier,actor_2_qcode=QCode,actor_2=QCode_name) ) %>%
  filter(!is.na(actor_1_qcode) & !is.na(actor_2_qcode) ) %>%
  mutate(source_root_target=paste0(src_country, "_", target_country) ) %>%
  mutate(
  event_date= lubridate::as_date(paste0( year, "-", month,"-",day ))
  )
dim(terrier_clean) #2,049,759

### 2022-02-07 replication_paper/rmd/ICBEdataset_figure_semantic_embeddings.Rmd
paper run1

```{r, messages=F, results='hide'}
library(reticulate)
py_discover_config()

#use_python("/home/skynet3/anaconda3/bin/python/")
use_python("/home/tlscherer/anaconda3/bin/python")

@@

#devtools::install_github("ropenscilabs/umapr")
library(umapr)
embedding <- umap(sentences_embedding)

>>>>

To set python, better to set it in ~/.Renviron. `use_python()` doesn't seem to work as desired. See [stackoverflow](https://stackoverflow.com/questions/50145643/unable-to-change-python-path-in-reticulate/58743111#58743111).

```{r, messages=F, results='hide'}
library(reticulate)
reticulate::py_discover_config()

#use_python("/home/skynet3/anaconda3/bin/python/")
#use_python("/home/tlscherer/anaconda3/bin/python3")

@@

#devtools::install_github("ropenscilabs/umapr")
library(umap)
library(umapr)
embedding <- umap(sentences_embedding)
